Deep Reinforcement Learning for Conservation Decisions

### 2021-10-15 manuscript/manuscript.Rmd
Adding some sections requested by MEE

>>>>

# Acknowledgements {-}

All authors were supported by the NSF Faculty Early Career Development Program Award 1942280. We thank Benjamin Blonder, Zachary Sunberg, and Claire Tomlin for their thoughtful comments.

# Conflicts of Interest {-}

The authors declare there is no conflict of interest.

# Authors' Contributions {-}

M.L. and C.B. developed the code and wrote the manuscript with support from K.E.A.N. and M.S.C.

# Data Availability {-}

We have created a github repository <https://github.com/boettiger-lab/rl-intro> that contains the code used to produce the figures.
